Toggle Smell Detection in Google Chrome

### 2015-12-08 paper/paper.tex
fixing tables

\documentclass[conference]{IEEEtran}
%\usepackage[top=1.2in, bottom=1.5in, left=0.8in, right=0.8in]{geometry}
\usepackage{balance}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{enumitem}

@@

\subsection{TOGGLE\_DEAD (Dead toggles)}

@@

 \\ \hline
\end{tabular}
\label{table:chrome-dir-data}
\end{table}

\begin{table}[ht]
\caption{Dead Toggle Smell}
\centering
\begin{tabular}{|p{1.5cm}|p{7cm}|}
\hline\hline
 Description & This smell is observed when one toggle flag is dependent on the state of one or more other toggle flags. \\ \hline

 Example & There are different patterns of this code smell similar to ``Message Chains''
 \begin{enumerate}
 \item{A variable might be used to store the state of the dependent toggles and will be used as a short circuit while checking the state of the actual feature flag.
 \begin{lstlisting} 
 boolean showF1Menu = ToggleService.isOn(“SHOW_F1_MENU”);

 if(showF1Menu && ToggleService.isOn(“SHOW_F1_F11_MENU”) {
 ….

 }
 \end{lstlisting}
 }

@@

 \\ \hline
 Consequences & Too many levels of nesting will add to the cost of testing the changes so as to cover all code paths with state on/off.
 \\ \hline

 Detection & This smell could be detected using the following approach.\\
 \begin{enumerate}
 \item{In order to identify potential positive instances of this smell, the detector could use trained patterns using a mathematical model like BLR(Binary Logistic Regression).}
 \item{Or simple level count could be used to identify the smell. Say for example if the number of nested toggles levels is greater than 2 then there is a possibility of the presence of this code smell.}
 \item{Also the detector can be enhanced to identify that there is a common master toggle used for the most of the nested toggles and could be prevented in identifying false smells.}
 \end{enumerate}

@@

\subsection{Mix of Compile time and run-time toggles)}

\begin{table}[ht]
\caption{TOGGLE\_MIX}
\centering
\begin{tabular}{|p{1.5cm}|p{7cm}|}
 \hline\hline
 Description & This smell is observed when the source code uses multiple techniques to manage toggles. One such usage is to combine compile time (\#define, \#ifndef) along with run time toggles.  \\ \hline

 Example & 
 \begin{lstlisting}
 //Location: /chrome/app/chrome_main_delegate.cc (Taken from Google chrome)
#if defined(OS_MACOSX)
// Mac needs them too for scrollbar related images and for sandbox
// profiles.
#if !defined(DISABLE_NACL)
process_type == switches::kNaClLoaderProcess ||
#endif
process_type == switches::kPpapiPluginProcess ||
process_type == switches::kPpapiBrokerProcess ||
process_type == switches::kGpuProcess ||
#endif
process_type == switches::kRendererProcess ||
process_type == switches::kUtilityProcess;
}
 \end{lstlisting}

>>>>

\documentclass[conference]{IEEEtran}
%\usepackage[top=1.2in, bottom=1.5in, left=0.8in, right=0.8in]{geometry}
\usepackage{balance}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{float}

@@

\subsection{TOGGLE\_DEAD (Dead Toggles)}

@@

 \\ \hline
\end{tabular}
\label{table:dead-toggle}
\end{table}

\subsection{TOGGLE\_NEST (Nested Toggles)}
\begin{table}[!htbp]
\caption{Nested Toggle Smell}
\centering
\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
\hline\hline
 Description & This smell is observed when one toggle flag is dependent on the state of one or more other toggle flags. \\ \hline

 Example & There are different patterns of this code smell similar to ``Message Chains''
 \begin{enumerate}
 \item{A variable might be used to store the state of the dependent toggles and will be used as a short circuit while checking the state of the actual feature flag.
 \begin{lstlisting} 
 boolean s = functionX();

 if(s && functionX()) {
    ...
 }
 \end{lstlisting}
 }

@@

@@

 Consequences & Too many levels of nesting will add to the cost of testing the changes so as to cover all code paths with state on/off.
 \\ \hline

 Detection & This smell could be detected using the following approach.
  \begin{enumerate}
 \item{In order to identify potential positive instances of this smell, the detector could use trained patterns using a mathematical model like BLR(Binary Logistic Regression).}
 \item{Or simple level count could be used to identify the smell. Say for example if the number of nested toggles levels is greater than 2 then there is a possibility of the presence of this code smell.}
 \item{Also the detector can be enhanced to identify that there is a common master toggle used for the most of the nested toggles and could be prevented in identifying false smells.}
 \end{enumerate}

\end{tabular}
\label{table:toggle-nest}
\end{table}
\newpage

\subsection{TOGGLE\_MIX (Mix of compile-time and run-time toggles)}

\begin{table}[h]
\caption{TOGGLE\_MIX}
\centering
\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
 \hline\hline
 Description & This smell is observed when the source code uses multiple techniques to manage toggles. One such usage is to combine compile time (\#define, \#ifndef) along with run time toggles.  \\ \hline

 Example & 
 \begin{lstlisting}
 #if
 process_type == switches::kNaClLoaderProcess ||
 #endif
 process_type == switches::kPpapiPluginProcess ||
 process_type == switches::kPpapiBrokerProcess
 #endif
 \end{lstlisting}
